---
title: "HK - Data 607 - Tidyverse Recipe - Part2"
author: "Habib Khan"
date: "November 30, 2019"
output: html_document
---

Note: This is extension of Lin Li's work on tidyverse recipe. Also I used head function to show the top rows rather than all rows to avoid ovewhelmed output

Create an Example.  Using one or more TidyVerse packages, and any dataset from fivethirtyeight.com or Kaggle, create a programming sample “vignette” that demonstrates how to use one or more of the capabilities of the selected TidyVerse package with your selected dataset. 



1. Get dataset from 538.



```{r}

weather <- read.csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/us-weather-history/KCLT.csv")
head(weather)
```


2. tidyr separate function:

```{r}

library(tidyr)

weather2 <- weather %>% separate(date, c("year", "month", "day"), sep = "-")
head(weather2)

```



3. dplyr select function:

```{r}

library(dplyr)
select(weather2, year, actual_mean_temp, record_min_temp, record_max_temp, record_precipitation)

```



4. dplyr filter (subsetting dataset)


```{r}

library(dplyr)
filter(weather2, year == "2014")
```


# Extension of work

Here, I am going to save another dataset after filtering the year and specific month and selecting the required columns


# Data manipulation

```{r}
library(knitr)
library(tidyverse)

weather_July2014 <- filter(weather2, year=="2014", month=="7") %>% 
  select(month, day, actual_min_temp, actual_max_temp)

kable(weather_July2014)
```

# Data visualization


## Minimum temperature in July 2014 on daily basis


```{r}
library(ggplot2)

ggplot(weather_July2014, aes(x=reorder(day, actual_min_temp), y=actual_min_temp))+geom_bar(stat="identity", fill="steelblue")
```



## Maximum temperature in July 2014 on daily basis


```{r}
ggplot(weather_July2014, aes(x=reorder(day, actual_max_temp), y=actual_max_temp))+geom_bar(stat="identity", fill="steelblue")
```


